Geometric signs reveal changes social structures and networks during the Western Eurasian Aurignacian

### 2025-06-09 paper/paper.qmd
fix that citation

The connectivity between sites represented in @fig-neighbor-net may reflect non-utilitarian mobility among these larger communities. Previous studies have shown a range of variation in magnitudes and types of mobility among hunter-gatherer groups [@Binford_1990; @Kelly_1983; @Johnson_2014; @Padilla-Iglesias_Bischoff_2024; @Singh_Glowacki_2022]. Non-utilitarian mobility establishes regional social networks which facilitate the spread of information and the survival of hunter-gatherers in uncertain environments [@Whallon_2006; @Fitzhugh_Phillips_Gjesfeld_2011; @Lovis_Donahue_2011; @Hitchcock_Ebert_2011; @Romano_Lozano_Fern2002]. The exchange and production of decorative items, such as objects with geometric signs, has been associated with non-utilitarian mobility and recognized as an indicator of social contact [@Whallon_2006; @Kelly_2024; @Kinahan_2013; @Newlander_2012; @Iizuka_Ferguson_Izuho_2022]. We can divide the connections depicted in @fig-neighbor-net into shorter-term information exchange and longer-term residential movement.

>>>>

The connectivity between sites represented in @fig-neighbor-net may reflect non-utilitarian mobility among these larger communities. Previous studies have shown a range of variation in magnitudes and types of mobility among hunter-gatherer groups [@Binford_1990; @Kelly_1983; @Johnson_2014; @Padilla-Iglesias_Bischoff_2024; @Singh_Glowacki_2022]. Non-utilitarian mobility establishes regional social networks which facilitate the spread of information and the survival of hunter-gatherers in uncertain environments [@Whallon_2006; @Fitzhugh_Phillips_Gjesfeld_2011; @Lovis_Donahue_2011; @Hitchcock_Ebert_2011; @Romano_Lozano_Fern2022]. The exchange and production of decorative items, such as objects with geometric signs, has been associated with non-utilitarian mobility and recognized as an indicator of social contact [@Whallon_2006; @Kelly_2024; @Kinahan_2013; @Newlander_2012; @Iizuka_Ferguson_Izuho_2022]. We can divide the connections depicted in @fig-neighbor-net into shorter-term information exchange and longer-term residential movement.
